\section{Taking Damage}
It's not uncommon that you take damage during combat.
After all, having an angry wizard throw fireballs at you is going to hurt!
This section describes the ways in which damage is taken, and what the consequences are.
See Section~\ref{sec:damage-resistance} for more info about damage resistance.

\subsection{Health Points (HP)}\label{sec:health-points}
Every character has a number of Health Points (HP).
The amount of HP a player has determines the player's level of consciousness:

\begin{center}
  \begin{tabular}{r | l}
    \textbf{HP Left} & \textbf{Effect} \\\hline
    $HP > 0$         & Alive and able to fight. \\
    $HP \leq 0$      & Roll against $2 \times Con$ to see if you faint. \\
    $HP \leq -MaxHP$ & Roll against $2 \times Con$ to see if you die.
  \end{tabular}
\end{center}

\paragraph{Note} Rolling against your $HP$ happens at the start of your turn.
  
\subsection{Fatigue Points (FP)}\label{sec:fatigue-points}
Fatigue is a different kind of damage.
One that affects you character more directly.
There are many different sources of fatigue: heat, starvation, dehydration, sleep deprivation, etc.

For every point of Fatigue lost, your character suffers a $-1$ penalty on all skill rolls.

\begin{center}
  \begin{tabular}{r | l}
    \textbf{FD Taken} & \textbf{Effect} \\\hline
    $FP \leq MaxFP/2$ & Roll against $MaxFP - FP$ to see if you faint. \\
    $FP \leq MaxFP$   & Immediately faint from exhaustion.
  \end{tabular}
\end{center}

\paragraph{Example} Charles has been walking the desert for the past five days.
The heat is getting to him, and he's lost 5 points of FP.
Charles has 10 FP, but due to the damage, he needs to roll 5 or less to not faint in the sand.
He rolls 9 and immediately collapses.