\chapter{Example Spells}
This chapter lists out a few example spells that could realistically be used in a game.
Again, please note that this is not by any means an exhaustive list.

\subsection{Breathe Foul Disease}
\textbf{Cost} 2 MP\\
\textbf{Requirements} Magic (Foul) specialisation. \\
\textbf{Range} 7m. \\
\textbf{Description} Target takes $d6$ Fatigue damage. 
Cannot be blocked or parried.

\subsection{Chill}
\textbf{Cost} 3 MP\\
\textbf{Requirements} Magic (Ice) specialisation. 
Diamond as catalyst. \\
\textbf{Range} Close\\
\textbf{Description} Inflicts $1d6$ Fatigue damage

\subsection{Create Object}
\textbf{Cost} 2 MP per half-pound (250g).\\
\textbf{Requirements} Magic (Creation) specialisation. Raw materials.\\
\textbf{Range} Close\\
\textbf{Description} The caster can transmute a raw material into anything of their choosing. 
-1 to cast for every additional half pound of material used, and for each layer of complexity on the final creation such as moving parts.

\subsection{Crumble}
\textbf{Cost} 5 MP per object affected.\\
\textbf{Requirements} Magic (Destruction) specialisation.\\
\textbf{Range} Close\\
\textbf{Description} Turns items to dust. 
-1 to cast for every additional item affected at once, and an additional -1 for large or well-crafted items.
The caster may only affect multiple items with this spell if they are in the possession of their target.

\subsection{Frostbite}
\textbf{Cost} 5 MP / Weapon\\
\textbf{Requirements} Magic (Ice) specialisation.
Diamond as catalyst\\
\textbf{Range} Close\\
\textbf{Description} Adds $d6$ fatigue damage to the affected weapon.

\subsection{Frozen Mist} 
\textbf{Cost} 3 MP / Square\\
\textbf{Requirements} Magic (Ice) specialisation. 
Diamond as catalyst\\
\textbf{Range} 6m\\
\textbf{Description} Blocks line of sights through affected squares. 
Deals $1d6-2$ fatigue damage for spending a turn inside an affected square.

\subsection{Grow}
\textbf{Cost} 5 MP for inanimate, 10 MP for animate.\\
\textbf{Requirements} Magic (Creation) specialisation. \\
\textbf{Range} Close\\
\textbf{Description} Doubles size of target item. 
Lasts five minutes.

\subsection{Icicle}
\textbf{Cost} 5 MP\\
\textbf{Requirements} Magic (Ice) specialisation. \\
\textbf{Range} 6m.\\
\textbf{Description} Deals $1d6+1$ damage.

\subsection{Soul Arrow}
\textbf{Cost} 1 MP per arrow\\
\textbf{Requirements} Magic catalyst\\
\textbf{Range} 20m\\
\textbf{Description} Shoots a bolt of soul energy at the target.
Deals $1d6 + Int$ damage.

\subsection{Weaken}
\textbf{Cost} 8 MP per die used.\\
\textbf{Requirements} Magic (Destruction) specialisation.\\
\textbf{Range} Close\\
\textbf{Description} Inflicts $d6$ fatigue damage per die used. 
-3 to cast for each additional die of damage.