\section{Adding New Rules}\label{sec:hacking-rules}
A lot of more complicated or complex rules are intentionally left out from the core rules in order to keep things simple.
Stuff like encumbrance, splitting mental and physical health, or even making special rules for vehicle-based combat come to mind.

You can add all those things in if you really want to, but should you?
Part of the appeal of a simpler system is to not be overburdened with complicated rules, and other RPG systems already exist that cater to people who yearn for simulating every detail.

If you wish to write a module adding more such things to the base game, please feel free to do so! Just keep in mind that the main ethos of \textit{Siren} is that of ease of use.

\subsection{Example Additions}

\paragraph{Encumbrance} Your character can comfortably carry weight up to $Con + Str$ kilograms. 
Every kilogram beyond that will add $1\mathit{FP}$ for every 20 minutes of carrying.

\paragraph{Mental Health} Mental health is $Con + Int$ and represents how much mental stress your character can suffer before negative effects start to show.
Mental Health functions the same way as physical health (\textit{HP}), except it can only be damaged by mental attacks.
Mental attacks can be anything from psionic attacks, to mental abuse, to being in a stressful environment your character doesn't feel comfortable in.
In a mundane setting Mental Health can replace \textit{MP} as outlined in Section~\ref{sec:traits-mp}.

\paragraph{Holding Your Breath} Your character can comfortably hold their breath for $Agi + Con$ seconds.
Every second beyond that requires a \textit{Constitution Save} to succeed.
If the save fails, your character will immediately gasp out for air and suffer whatever consequences doing so may entail.