\documentclass[a4paper]{book}
\input{preamble.tex}

\title{Siren - Simple RPG Engine $\beta1.0.1$}
\author{By Niko Lepka}
\date{\today}

\begin{document}

\maketitle

\chapter*{Preface}
\section*{What is Siren?}
Siren, the \textbf{Si}mple \textbf{R}PG \textbf{En}gine, is an RPG system that aims at being simple and easy to learn without also compromising on the expressiveness of the system.

An RPG engine, much like a video game engine, is a framework on which you can build your own system. If any of the rules in this seem like they don't \textit{quite} fit what you need, you're free to change them for your campaign

\section*{What are RPGs?}
Role Playing Games, or RPGs for short, are games in which you take the role of some character and act in their stead.
You may know this from video games, where you play some adventurer in a medieval land full of magic and dragons; or where you play a person that's trying to survive in a nuclear wasteland, fighting mutants and warring factions.
But RPGs date back before that.

Traditional RPGs, also known as \textit{Tabletop RPGs} or \textit{Pen and Paper RPGs} date back to the early 1970s.
It's a social game played with a group of friends around a table, mutually telling a common story of great adventure, mysticism, space warfare or whatever they can come up with.

\section*{Who is this for?}
Some role-playing systems have hundreds of books and rules, so many so that it's hard to remember them all, and valuable playtime is spent looking up rules. 
While other systems have so few and vague, that a lot of playtime is spent arguing about which rules apply to a given situation.

Siren is made for those players who wish to have a small yet precise set of rules that can be used in every type of story, whether it's a grand space opera, or high fantasy, Siren's got you covered.

\section*{Conventions}
This book uses standard RPG dice notation, which looks like this: $AdX\pm L$, where $A$ is the number of dice, $X$ is the number of faces on the die, and $L$ is the value added or subtracted after the roll, so $3d6+8$ means roll three six-sided dice, and add 8 to the result.
\paragraph{Note} Notes are displayed like this, and often convey important information to the player or GM regarding a certain mechanic.
\paragraph{Example} Examples are displayed like this, and show a situation in which something is used.

\newpage
\section*{Special Thanks}
Special thanks to the lovely individuals who've helped out with the project:
\begin{center}
    \begin{tabular}{cccc}
        Aleksander Øglænd & Christian J. Martinsen & Marco L.L. Olsen & Morten M. Rasmussen \\
        Patrick A. & Thomas G. McCollin \\
    \end{tabular}
\end{center}

\section*{Licence}
This work is licensed under the Creative Commons Attribution-ShareAlike 4.0 International License.
To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/4.0/ or send a letter to Creative Commons, PO Box 1866, Mountain View, CA 94042, USA.

\tableofcontents

\input{chapters/basics.tex}
\input{chapters/game-creation.tex}
\input{chapters/character-creation.tex}
\input{chapters/traits.tex}
\input{chapters/skills.tex}
\input{chapters/exploits.tex}
\input{chapters/magic.tex}
\input{chapters/combat.tex}
\input{chapters/defence.tex}
\input{chapters/character-progression.tex}

\input{chapters/appendix.tex}
\end{document}
